From Education to Entrepreneurship

### 2014-12-02 index.Rmd
Added lib and fixed index page
Realized ggvis isn't interactive w/ knitted docs, changed web content

# Variation in Perceived Opportunities in OECD
```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#fff7bc', '#d95f0e']"
))

@@

# Distribution of Perceived Opportunities in OECD Countries

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

D4 %>% 
  ggvis(~mean, fill := "#2c7fb8") %>% 
  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
                   center = input_slider(0, 2, step = 0.05, label = "center"))

>>>>

### Variation in Perceived Opportunities in OECD
```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#fff7bc', '#d95f0e']"
))

@@

<br>

<br

### Distribution of Perceived Opportunities in OECD Countries

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library(ggvis)

D4 %>% ggvis(~mean, fill := "#2c7fb8") %>% layer_histograms(width = 0.2)

#D4 %>% 
 # ggvis(~mean, fill := "#2c7fb8") %>% 
  #layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
   #                center = input_slider(0, 2, step = 0.05, label = "center"))
